### 2024-08-19 README.Rmd
Add DOI link in README to genomic data
revision2: Modify Readme to point to most recent code and analyses for this project

pvdiv-phenology-gxe contains the non-genomic data and code used to analyze the genetics of GxE in the phenology data collected for the switchgrass diversity panel in 2019, including green-up dates and flowering dates in 2019. This repository will be private until the associated manuscript is published.

In general, if you have any questions about how to locate an analysis folder or code used for an analysis, look at this README first. Then, if you still have questions, feel free to open a pull request with your issue and I will be happy to help.

@@

    - Data objects and draft figures created as part of the analysis of heritability (including variance components analysis, done in ASReml), genome-wide association (on phenotypic BLUPs, done using the switchgrassGWAS R package), and mash (on results from the univariate GWAS, done using the switchgrassGWAS R package). Generally, the code to replicate these analyses can be found in the R/ directory.

@@

    - Contains the majority of the code used in the manuscript (some additional code used to prepare data is in data-raw/.) 
    - Files that start with "Plots" were used to make manuscript figures
    - Files that start with "nohup" were used to run mash
    - Files that start with "Analysis" were used to generate files in the analysis/ folder. I tried to name these descriptively but there are a lot of them; please open a pull request if you want help locating specific code.

@@

    - Contains completed drafts of a manuscript on the genetics of GxE in phenology in the switchgrass diversity panel.

>>>>

pvdiv-phenology-gxe contains the non-genomic data and code used to analyze the genetics of GxE in the phenology data collected for the switchgrass diversity panel in 2019, including green-up dates (the timing of vegetative growth) and flowering dates (the timing of reproductive growth) in 2019.

The **most recent submission** is on bioRxiv: https://doi.org/10.1101/2021.08.19.456975

**Code** used in the 2024 submission is located here: https://github.com/Alice-MacQueen/pvdiv-phenology-gxe/blob/main/R/Analysis_v1.2_mash_using_greedy_covar.qmd.

You can find the **genomic data** at: https://doi.org/10.18738/T8/A604BU.

In general, if you have any questions about how to locate an analysis folder or code used for an analysis, look at this README first. Then, if you still have questions, feel free to open a pull request with your issue or contact me directly at alice.macqueen[at]gmail.com and I will be happy to help.

@@

Data objects and draft figures created as part of different discrete analyses, including:

    - heritability/ contains the analysis of heritability (including variance components analysis, done in ASReml);
    - gwas/BLUPs/  contains genome-wide association results (on phenotypic BLUPs, done using the switchgrassGWAS R package);
    - hypothesis_matrices/ contains unpublished analyses of correlation data between GxWeather matrices, used as exploratory plots for a revision;
    - mash/ contains mash models (on results from the univariate GWAS, done using the switchgrassGWAS R package). 
    - mash_greedy_algorithm/mash_h2_diag_covar/ contains runs of the greedy mash algorithm used to select covariance matrices for inclusion in the mash model for the current revision. mash_greedy_algorithm/ also contains other runs of the greedy mash algorithm used as exploratory analyses for suitability for the revision.

Generally, the code to replicate these analyses can be found in the R/ directory.

@@

R/ contains the majority of the code used in the manuscript (some additional code used to prepare data is in data-raw/.)

    - The file titled "Analysis_v1.2_mash_using_greedy_covar.qmd" contains all of the code used to run the analyses and generate the figures for the 2024 revision (in manuscript/revision2/). 
    - THe file titled "SI_Appendix_Datasets.Rmd" contains the code used to generate the SI Appendix datasets and the SI Appendix figures for the 2024 revision.
    - The file titled "UT_Dataverse_files.Rmd" was used to generate the SNP datasets uploaded to the UT Dataverse for replication of this analysis. 
    - Files that start with "Plots" were used to make manuscript figures for a 2021 submission
    - Files that start with "nohup" were used to run mash for a 2021 submission
    - Files that start with "Analysis" were used to generate files in the analysis/ folder. I tried to name these descriptively but there are a lot of them; please open a pull request if you want help locating specific code from earlier versions of this analysis. The most recent version is in the file titled "Analysis_v1.2_mash_using_greedy_covar.qmd".

@@

This folder contains completed drafts of a manuscript on the genetics of GxE in phenology in the switchgrass diversity panel.

    - revision2/ contains the most recent, 2024 revision. The main text is called revision2.pdf. There are also folders containing pdfs of the response to reviews (in response_to_reviews/), the SI Appendix data (in SI_Appendix) and images used in the main manuscript (in images/).
    - Coauthors/ contains the manuscript from a submission in 2021.
